Democratizing Secure Two-Party Computation

### 2017-10-12 OaklandSubmission/intro.tex
chat-bot

\section{Introduction}
\label{sec:intro}
Today it is hard for developers to create secure implementations using cryptographic techniques.
Typical developers lack an understanding of cryptography protocols
and cannot be expected to implement them correctly without tool support.
In an ideal world, a developer declares the functionality to be implemented
in a general purpose programming language and an automatic tool takes care
of all the cryptography and generates a secure and efficient implementation  of the functionality. 
This paper provides a language-based solution to make
secure multiparty computation (SMC) accessible to the software developer community. \nc{Why do we call it SMC? A bit non-standard for crypto audiences isnt it?}

@@

Suppose a developer wants to compute $w^Tx >0$ securely using SMC. With the current techniques, he has two options. \nc{The two options appear quite far apart in the text. Can we make bullet points maybe?} He can code up the functionality in a programmer friendly domain-specific language such as \cite{lambdaps,wysteria,oblivm} that would automatically compile it to an SMC protocol. The downside is that all of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of complex trade-offs between arithmetic and boolean cryptographic schemes. In their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate conversion gates. In short, as is also mentioned by the authors themselves, the current system is not suitable to be used by non-specialist programmers. \nc{Also say that the programmer would need to know which functionality is better suited for arithmetic/boolean and also how to split the complete functionality into such parts.} \divya{Change tone...}
Our work .....
\nc{Should we also say here that a third option is to hire a cryptographer and build specific crypto protocols for the functionalities? :) This seems to be the option we are targetting when we show our comparisons and we say that we beat or match hand-crafted protocols}

@@

In this work, we develop and implement our framework \tool \nc{I still like EasyPC :)} for secure computation that achieves generality, performance and programmer productivity. The programmer writes a high level C-like program (instead of a circuit) to describe the function to be computed. Our compiler automatically generates an SMC protocol using a mix of Arithmetic and Boolean compute. Our compiler is general and can work with any secure implementation of a mix of arithmetic and boolean computations. In our work, we focus on semi-honest secure two-party computation. We build on ABY \cite{aby} that provides the suitable cryptographic back-end in this setting. We provide a formal type system and prove correctness and security of our compiler. We evaluate our system on various benchmarks such as logistic regression and convolutional neural network (CNN) for MNIST data \cite{minionn}, naive bayes, decision trees from \cite{shafindss}. Evaluations show that protocols generated by our compiler match the performance of hand-crafted protocols in most cases (see \sectionref{sec:eval}). \divya{Below, we will  give an overview of \tool and describe our contributions in more detail.}

@@

\subsection{\tool: Overview and Contributions} 
\label{sec:contrib}
%Write high level overview of programming language and tool.. \divya{have some preamble}

\tool is a programmer-friendly framework to express the function to be computed and uses a mix of arithmetic and boolean SMC back-ends. We illustrate the above toy example of $w^Tx >0$ in our language in \figureref{ex-sml}. As is clear from the code, the programmer is not required to write keywords such as {\em secret} or {\em public} and can remain completely oblivious of the cryptographic back-end. In contrast, \figureref{ex-aby} illustrates the same example using the framework in ABY \cite{aby}. Here, as already mentioned, the programmer needs to write the low level gates like $\mathrm{MULT, ADD, CONS, GT}$, etc. The programmer is also required to use the appropriate share conversion gates such as A2Y that converts Arithmetic shares to Yao shares.

@@

We give a formal {\em type system} for our language and prove useful properties. We prove that if a program type checks in our language then it would run correctly, e.g., there would not be any array index out of bounds error. The programmer writes a single code describing the inputs from each party and the function to be computed. Our compiler automatically generates separate executables for the server and the client that can be executed in the distributed setting. We prove the {\em correctness} for this compilation, i.e., the outputs obtained in the distributed execution are identical to the stand-alone execution by a trusted third party. We formally reduce the {\em security} of our system to the security of the cryptographic back-end. For details on formal language, correctness and security theorems see \sectionref{ld}.
\nc{Shall we have paragraph heads or someting to outline the different contributions? Above feels like one big story.}

@@

\input{fig-ex-aby}
\input{fig-ex-sml}

>>>>

\section{Introduction}
\label{sec:intro}
Today it is hard for developers to create secure implementations using cryptographic techniques.
Typical developers lack an understanding of cryptography protocols
and cannot be expected to implement them correctly without tool support.
In an ideal world, a developer declares the functionality to be implemented
in a general purpose programming language and an automatic tool takes care
of all the cryptography and generates a secure and efficient implementation  of the functionality. 
This paper provides a language-based solution to make
secure multiparty computation (SMC) accessible to the software developer community. \nc{Why do we call it SMC? A bit non-standard for crypto audiences isnt it?} \divya{I drank my tears and a part of me died when I did this. Apparently thats what it is called outside the theory community.}

@@

Suppose a developer wants to compute $w^Tx >0$ securely using SMC. With the current techniques, he has two options. \nc{The two options appear quite far apart in the text. Can we make bullet points maybe?} \divya{Bullet list would look bad. I tried listing both options first and then discussing but its hard to talk about ABY before.} He can code up the functionality in a programmer friendly domain-specific language such as \cite{lambdaps,wysteria,oblivm} that would automatically compile it to an SMC protocol. The downside is that all of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of complex trade-offs between arithmetic and boolean cryptographic schemes. In their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate conversion gates. In short, as is also mentioned by the authors themselves, the current system is not suitable to be used by non-specialist programmers. \nc{Also say that the programmer would need to know which functionality is better suited for arithmetic/boolean and also how to split the complete functionality into such parts.} \divya{Change tone...}
Our work .....
\nc{Should we also say here that a third option is to hire a cryptographer and build specific crypto protocols for the functionalities? :) This seems to be the option we are targeting when we show our comparisons and we say that we beat or match hand-crafted protocols} \divya{We can do this! wMight have to see the flow.}

@@

In this work, we develop and implement our framework \tool \nc{I still like EasyPC :)} \divya{I agree that \tool is bad. What would be the full form for EasyPC? Shouldn't it be EasySC?} for secure computation that achieves generality, performance and programmer productivity. The programmer writes a high level \divya{C-like} program (instead of a circuit) to describe the function to be computed. Our compiler automatically generates an SMC protocol using a mix of Arithmetic and Boolean compute. Our compiler is general and can work with any secure implementation of a mix of arithmetic and boolean computations. In our work, we focus on semi-honest secure two-party computation. We build on ABY \cite{aby} that provides the suitable cryptographic back-end in this setting. We provide a formal type system and prove correctness and security of our compiler. We evaluate our system on various benchmarks such as logistic regression and convolutional neural network (CNN) for MNIST data \cite{minionn}, naive bayes, decision trees from \cite{shafindss}. Evaluations show that protocols generated by our compiler match the performance of hand-crafted protocols in most cases (see \sectionref{sec:eval}). \divya{Below, we will  give an overview of \tool and describe our contributions in more detail.}

@@

\subsection{\tool: Overview and Contributions} 
\label{sec:contrib}
%Write high level overview of programming language and tool.. \divya{have some preamble}
\divya{I can add paragraph headings..}

\tool is a programmer-friendly framework to express the function to be computed and uses a mix of arithmetic and boolean SMC back-ends. We illustrate the above toy example of $w^Tx >b$ in our language in \figureref{ex-sml}. As is clear from the code, the programmer is not required to write keywords such as {\em secret} or {\em public} and can remain completely oblivious of the cryptographic back-end. In contrast, \figureref{ex-aby} illustrates the same example using the framework in ABY \cite{aby}. Here, as already mentioned, the programmer needs to write the low level gates like $\mathrm{MULT, ADD, CONS, GT}$, etc. The programmer is also required to use the appropriate share conversion gates such as A2Y that converts Arithmetic shares to Yao shares.

@@

We give a formal {\em type system} for our language and prove useful properties. We prove that if a program type checks in our language then it would run correctly, e.g., there would not be any array index out of bounds error. The programmer writes a single code describing the inputs from each party and the function to be computed. Our compiler automatically generates separate executables for the server and the client that can be executed in the distributed setting. We prove the {\em correctness} for this compilation, i.e., the outputs obtained in the distributed execution are identical to the stand-alone execution by a trusted third party. We formally reduce the {\em security} of our system to the security of the cryptographic back-end. For details on formal language, correctness and security theorems see \sectionref{ld}.
\nc{Shall we have paragraph heads or something to outline the different contributions? Above feels like one big story.}

@@
